Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
more changes; questions

This section presents important background material for the rest of the paper.

@@

Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest.  Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
  static
  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\comments{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

\section{Approach}
\label{sec:approach}

%% \Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
%%   falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
%%   de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
%%   loop aninhado ao loop ``for every k'' que o lithium-slicer
%%   implementa (algo como ``for every k and every failing test'')?  Caso
%%   vc. faca slice contra um teste particular, vc. garante (checa saida)
%%   que os demais testes que originalmente falhavam continuam falhando
%%   pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
%%   de inicio.}

%% \Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
%% ferramenta chama o lithium tantas vezes como o número de casos de teste
%% que falham para cada versão do projecto. Assumindo que o numero de casos de
%% testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
%% 5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada
%% teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de
%% executar a nossa ferramenta para uma versão do projecto que os
%% testes que aparecem na pasta da versão do projecto são os mesmos quando corro
%% o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
%% oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
%% antes de correr as experiências eu corri o defects4j para obter as mensagens
%% esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
%% que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
%% realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
%% ao pseudocode eu diria que é for every $k$ and every failing test.}

\subsection{The \sfl{}+\cs{} combination}
\label{sec:comb}

To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

>>>>

This section discusses  important background material for the rest of the paper.
\Rui{not very happy with this sentence.}

@@

\Rui{intro needs to refer to Critical Slicing, somehow..}
\Rui{Are we the first to use Critical Slicing in combination? Say so, if this
is the case.}
Program slicing is a program understanding technique to identify the
relevant parts of the program with respect to given points of
interest.  Dynamic
slicing~\cite{Agrawal:1990:DPS:93542.93576}\comments{~--~as opposed to
  static
  slicing~\cite{Weiser:1981:PS:800078.802557}~--~~\cite{Binkley:2014:OLP:2635868.2635893}}
has been shown useful in automated software debugging where the region
of interest is restricted to what can be reached from failing
tests. Several dynamic slicing techniques exist. This paper uses
Critical Slicing (\cs{})~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\comments{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\comments{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing simplifies the original
program such that the resulting program preserves critical
observations, such as assertion violations. More precisely, the
simplification mechanism consists of deleting statements on the
original program and checking if the output of the original and
modified program are the same.

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \Rui{site}.

@@

\section{The \comb{} Approach}
\label{sec:approach}

\Rui{add a sentence?}

\subsection{Combinging \sfl{} with \cs{}}
\label{sec:comb}

To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).
